SHARP - II. Beware the effect of edge-on discs when interpreting the anomalous flux-ratios of gravitationally lensed quasars

### 2015-09-07 papers/B1555_EdgeOn/B1555_letter.tex
update comments from Leon and Dandan also bib file

\begin{abstract}
Gravitational lens flux-ratio anomalies provide a powerful technique for measuring dark matter substructure in distant galaxies. However, before using these flux-ratio anomalies to test galaxy formation models, it is imperative to ascertain that the given anomalies are indeed due to the presence of dark matter substructure and not due to some other non-smooth component of the lensing galaxy halo. Here we present the case of CLASS~B1555+375, which has a strong radio-wavelength flux-ratio anomaly, but where the lensing galaxy is also revealed in high resolution infrared imaging with the W. M. Keck-II Telescope and the {\it Hubble Space Telescope} to have a clear edge-on disc component that crosses directly over the pair of images that exhibit the flux-ratio anomaly. We find simple models that include the disc can reproduce the cm-wavelength flux-ratio anomaly without requiring additional dark matter substructure. Although further studies are required, our results suggest the assumption that all flux-ratio anomalies are due to a population dark matter sub-haloes may be incorrect, and analyses that do not account for the full non-smooth component of the lens macro-model will likely overestimate the substructure mass fraction in massive lensing galaxies.
\end{abstract}

@@

It was first suggested by \citet{Mao1998} that the flux-ratio anomalies observed in the multiple radio-loud images of lensed quasars could be interpreted as a sign of the presence of substructure in lens galaxies. Indeed, small perturbations in the gravitational potential are sufficient to cause flux-ratio anomalies in gravitationally lensed systems \citep{metcalf01,Dalal2002,Bradac02}, particularly for those systems with a close pair of merging images \citep{KD04}. At radio wavelengths, the lensed images are neither sensitive to micro-lensing from stars (\citealt{K03}; although see \citealt{koopmans00}), nor to dust extinction. Also, any variation in the properties of the radio images that are due to propagation effects (e.g. interstellar scattering or free-free absorption) have a well understood frequency dependence that can be identified and accounted for (e.g. \citealt{biggs03,M07,winn04}). This makes the flux-ratio anomalies of radio-loud lensed images a promising tool to detect and measure dark matter substructures in a large sample of distant galaxies \citep{Dalal2002}. However, a recent comparison of the observational data (8 gravitational lens systems with four or more images) with the expectations from a set of cold dark matter simulations, which are also representative of the mass and redshift of the lens galaxies, suggest that there is only a 1--4 per cent probability that the observed flux-ratio distribution is produced only by substructure \citep{Xu14}.

The \emph{gravitational imaging technique}, which alternatively utilizes the surface brightness distribution of extended arcs and Einstein rings to detect low-mass substructures within lensing haloes, was introduced by \citet{K05} and \citet{V09}. This method gives a measurement of the substructure mass fraction for a sample of 10 lensing galaxies that is currently in agreement with the theoretical expectations from cold matter matter simulations \citep{V14a,V12}. The reason for the conflicting results between the flux-ratio anomaly and gravitational imaging techniques is not currently clear.  While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than substructure \citep[see][for a discussion]{Xu14}.

@@

Here we focus on CLASS B1555+375 \citep{Marlow99}, which was discovered as part of the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2}. B1555+375 has four lensed images with a maximum separation of 426~mas in a fold-configuration, where the two merging lensed images show a strong and persistent flux-ratio anomaly at radio wavelengths; previous radio monitoring observations ruled out microlensing effects as the cause of the anomaly \citep{K03}. As B1555+375 was included in the observational and theoretical analyses of both \citet{Dalal2002} and \citet{Xu14}, understanding its mass distribution is of key importance to assess any systematics with the inferred level of substructure in the lensing halo with the flux-ratio anomaly method. The SHARP imaging data are introduced in Section 2 and we present a revised lens model using these data in Section 3. The results of this analysis and their implications are discussed in Section 4. Note that the redshifts of both the lens galaxy and the lensed source are unknown for B1555+375, so we assume redshifts of $z_l = 1$ and $z_s = 1.5$, respectively, due to their red colours \citep{Marlow99}. This assumption has no effect on the derived magnifications or flux-ratios of our analysis.

@@

Our dataset consists of optical and infrared imaging taken with the W. M. Keck-II Telescope and the {\it HST}, and high-resolution radio imaging taken with the Very Long Baseline Array (VLBA), which are discussed below and are summarized in Table~\ref{tab:obs}.

@@

There are several notable features in the high-resolution AO and {\it HST} data. These include the nearly complete lack of emission associated with lensed images B and D, as can be seen by comparing the radio contours to the $K^\prime$-band emission, and the faint, but clearly visible emission from what appears to be an edge-on lensing galaxy, with a position angle of $\sim 10$~deg and an ellipticity of $\sim 0.8$. We note that this position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D. Therefore, the lack of emission that is seen from these images is likely due to dust extinction.

@@

The flux-ratio anomaly and relative sizes of the images at radio-wavelengths implies that there must be some form of perturbation to the gravitational lens mass model, which has thus far been attributed to dark matter substructure within the lensing galaxy or along the line-of-sight to the lensed images \citep{Dalal2002,Xu14}. However, our high-resolution near infrared imaging suggests the intriguing possibility that the mass perturbation could be due to an edge-on disc component within the lens. To test this possibility, we model the system with a disc component in order to see if a plausible mass model can explain the flux-ratio anomaly, without the need for additional substructure.

We use the lens modelling code {\sc gravlens} \citep{Kee01} to model the compact radio components. The inputs to the model are the observed image positions measured from the MERLIN radio observations of \citet{Marlow99} as all of the images are significantly detected in these data. The flux-ratio measurements are taken from \citet{K03}, who used half a year of MERLIN monitoring to obtain flux-ratio curves. In total, there are 11 constraints to the mass model provided by the observational data. As a first trial of modelling, we re-create the singular isothermal ellipsoid (SIE; 7 free parameters) model of \citet{Marlow99} to check the performance of a simple lensing potential. Consistent with previous studies \citep{Marlow99,Xu14}, a single elliptical potential model cannot reproduce the observed flux-ratios in B1555+375 (see Table~\ref{tab:results}; reduced $\chi^2 =97.3$).

The next step is to examine if an edge-on disc can cause a physically plausible perturbation in the strong lensing mass model that results in the observed flux ratio anomaly of  merging images A and B. An exponential disc profile best describes the disc component in spiral galaxies because it matches the light distribution \citep{Kee98}. We thus choose a SIE plus an exponential disc model (SIE+ExpDisc) in our study of B1555+375. The free parameters of the model are the SIE Einstien radius ($b$), centroid position, ellipticity ($e$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$), and scale length ($R_s$). A Detailed definition of these mass profiles is described by \citet{Kee01}. The source position adds two additional model parameters. We have not included a third component such as an external shear or an NFW halo because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model. Significantly deeper observations at a higher bandwidth with current very long baseline interferometric arrays will test more complex models in the future by imaging the extended gravitational arc and more significantly detecting image D.

@@

The best-fit model parameters are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:model}. Table \ref{tab:results} also shows the comparison between the observed radio data and the model predicted image positions and flux ratios. We find that by adding an elongated exponential disc to a smooth potential model there is significant improvement in the predicted flux-ratios when compared to the results for the SIE-only model, with a reduced $\chi^2 = 2.7$. The positions are all in agreement, and the flux-ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B. The mass model requires that the exponential disc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable. We note that there is a significant 0.036~arcsec offset between the SIE and exponential disc components, which is likely due to there being an additional ellipticity in the model (e.g. from an external shear) that is being partly compensated for by the disc component. Again, more complex mass models that use the full extent of the gravitational arc and the compact lensed images from future high resolution radio imaging will be able to confirm this.

@@

Although flux-ratio anomalies provide a powerful tool to investigate low-mass substructure in lensing haloes out to cosmological redshifts, it is clear that some care is needed in interpreting the results. It is now well established that observations of radio-loud gravitational lenses provide the most robust observational constraints because they are less affected by dust extinction and microlensing, and monitoring can determine the best estimate of the intrinsic flux ratios. This has led to an often studied sample of eight radio-loud gravitational lenses with well-defined flux-ratio measurements that are most likely due to perturbations from a smooth mass distribution \citep{Xu14}. In general, lens models that are based only on the locations of lensed radio-loud images have large degeneracies due to the limited number of constraints that are provided by 50 to 200~mas imaging of the unresolved sources \citep[e.g.][]{Ka91}. Furthermore, the nature of the perturbation may not be due exclusively to a population of low-mass substructures as as been already shown to be the case for MG J0414+0534 and MG J2016+112, where there is evidence for luminous companion dwarf galaxies that can account for the observed flux ratios, and even observed astrometric anomalies (\citealt{ros00,chen07,more09}; see also \citealt{mckean07,jackson10}).

Here, we find evidence for an edge-on disc in the flux-ratio anomalous gravitational lens B1555+375 that can also account for the required perturbation in the mass model. Such high-order deviations from a smooth mass distribution have already been suggested \citep{evans03,congdon05}, but this is the first time that a disc has been observed and modelled to account for a flux-ratio anomaly. However, it is important to realise that by including observationally motivated perturbations like luminous dwarf companions or edge-on discs in the mass models, we are still limited in our interpretation since we must assume that the anomalies are due exclusively to these additional components. For B1555+375, it may be possible to independently constrain the mass of the disc through kinematic measurements (most likely from mm-wavelength resolved emission line observations), which would test whether the disc makes a sufficient contribution to the mass model (e.g. as in the case of B1933+503; \citealt{suyu12}). Also, as we have shown here, B1555+375 shows evidence for an extended $\sim100$~mas gravitational arc at radio-wavelengths that crosses the edge-on disc. Further high resolution imaging with very long baseline interferometry will provide the observational constraints required to fully test whether the extended disc is sufficient to cause the anomaly. Nevertheless, before concluding that the flux-ratios in any given lens system are a result of substructure, it is critical to explore a range of smooth models that are informed by additional observations or to do a comprehensive analysis such as that conducted by \citet{Xu14}. Otherwise, the derived substructure fractions should be considered as upper limits.

@@

%In this letter, we instead focus on the effect that more complicated lens galaxy mass distributions \textbf{have} on flux-ratio anomalies. Traditionally, flux-anomalous lensed quasars have been radio-loud, initially discovered in radio observations. While radio data provide reliable information on the positions and the fluxes of the lensed images, they are often unable to detect the lens galaxies. Moreover, lens modelling based only on the positions of the four images can be highly degenerate and prior assumptions play a key role in the interpretation of the observed flux-ratio anomaly.  Since lens galaxies are typically at redshifts of $z \leq 1$, optical and near-infrared observations are ideal for measuring the light distribution of lens galaxies and obtaining useful prior information on the underlying mass distributions. Indeed \citet{SHARP12} showed that high resolution IR imaging can help to significantly improve the precision of the lens modelling. This improvement is even more dramatic in the case of B1555+375, where HST and SHARP AO high resolution imaging has allowed us to detect, for the fist time, the presence of an edge-on disk. This newly discovered edge-on disk provides a strong prior for our lens modelling.  With an additional disk component, our model matches to both the radio image positions and their flux-ratio, wheras models with only one SIE component \citep{Marlow99,Xu14} fail to reproduce the fluxes correctly. Our successful modelling indicates that the kpc-scale structure of the lens galaxy itself is sufficient to explain the flux-ratio anomalies in B1555+375, without any need to invoke the presence of substructure.

%From a theoretical perspective, \citet{Xu14} also find that substructures cannot explain the observed radio flux anomalies in all the gravitational lenses that were considered. After adding sub-haloes from numerical simulations to these systems, only one out of the eight radio-loud gravitational lenses achieves the level of the flux-ratio anomalies seen in the observations.  The rest are unlikely (only $1 - 4$ per cent probability) to have an observed distribution of flux-ratio anomalies produced only by substructure, including our target B1555+375. In fact, among those eight radio lenses, B1555+375 is one of the most anomalous gravitational lenses, but it is also one of the most challenging systems to explain by substructures. \citet{Xu14} have concluded that the failure in predicting flux-ratios is most likely due to an oversimplified/improper lens modelling, which is consistent with the results of this letter. They also point out that the SIE component and the external shear in their model are orthogonal, indicating a possible missing ingredient in the lens model. Indeed, it's hard to find physical interpretation for an large and orthogonal external shear, without the inclusions of an observationally motivated edge-on disc component.

Our results for B1555+375 clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of compcat lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies. While upcoming large-scale surveys with the Dark Energy Survey, Kilo-Degree Sky-VIKING, Square Kilometre Array, {\it Euclid}, and Large Synoptic Survey Telescope, are expected to deliver new large samples of gravitationally lensed quasars, in the near future the discovery of new systems using narrow-line quasar emission \citep{N14} will provide a new and invaluable statistical perspective on the current constraints based on flux-ratio anomalies. We stress, therefore, that one should be very careful when interpreting the nature of flux-ratio anomalies, as prior simple assumptions on the lens mass distribution are a significant source of bias.

Our analysis shows that in order to derive a precise quantification of the substructure population and any derived properties from strongly lensed flux-ratio anomalies, it is crucial to have a careful estimation of non-substructure effects, such as galaxy discs and nearby massive satellites. In fact, even in the presence of mass substructures, the observed flux-ratio anomalies could be still dominated by the complex structure of the lens galaxy. Finally, additional near-infrared AO imaging from SHARP shows that B1555+375 is not the only gravitational lens having a significant disc component detection in the lensing galaxy.  These gravitational lenses will be investigated in a future work, but the images alone strongly suggest that other systems may have similar links between flux-ratio anomalies and disc components.

>>>>

\begin{abstract}
Gravitational lens flux-ratio anomalies provide a powerful technique for measuring dark matter substructure in distant galaxies. However, before using these flux-ratio anomalies to test galaxy formation models, it is imperative to ascertain that the given anomalies are indeed due to the presence of dark matter substructure and not due to some other non-smooth component of the lensing galaxy halo or other propagation effects. Here we present the case of CLASS~B1555+375, which has a strong radio-wavelength flux-ratio anomaly, but where the lensing galaxy is also revealed in high resolution infrared imaging with the W. M. Keck-II Telescope and the {\it Hubble Space Telescope} to have a clear edge-on disc component that crosses directly over the pair of images that exhibit the flux-ratio anomaly. We find simple models that include the disc can reproduce the cm-wavelength flux-ratio anomaly without requiring additional dark matter substructure. Although further studies are required, our results suggest the assumption that all flux-ratio anomalies are due to a population dark matter sub-haloes may be incorrect, and analyses that do not account for the full non-smooth component of the lens macro-model will likely overestimate the substructure mass fraction in massive lensing galaxies.
\end{abstract}

@@

It was first suggested by \citet{Mao1998} that the flux-ratio anomalies observed in the multiple radio-loud images of lensed quasars could be interpreted as a sign of the presence of substructure in lens galaxies. Indeed, small perturbations in the gravitational potential are sufficient to cause flux-ratio anomalies in gravitationally lensed systems \citep{metcalf01,Dalal2002,Bradac02}, particularly for those systems with a close pair of merging images \citep{KD04}. At radio wavelengths, the lensed images are neither sensitive to micro-lensing from stars (\citealt{K03}; although see \citealt{koopmans00}), nor to dust extinction. Also, any variation in the properties of the radio images that are due to propagation effects (e.g. interstellar scattering or free-free absorption) have a well understood frequency dependence that can be identified and accounted for (e.g. \citealt{biggs03,M07,winn04}). This makes the flux-ratio anomalies of radio-loud lensed images a promising tool to detect and measure dark matter substructures in a large sample of distant galaxies \citep{Dalal2002}. However, a recent comparison of the observational data (eight gravitational lens systems with four or more images) with the expectations from a set of cold dark matter simulations, which are also representative of the mass and redshift of the lens galaxies, suggest that there is only a 1--4 per cent probability that the observed flux-ratio distribution is produced only by substructure \citep{Xu15}.

The \emph{gravitational imaging technique}, which alternatively utilizes the surface brightness distribution of extended arcs and Einstein rings to detect low-mass substructures within lensing haloes, was introduced by \citet{K05} and \citet{V09}. This method has given a measurement of the substructure mass fraction for a sample of 10 lensing galaxies that is currently in agreement with the theoretical expectations from cold matter matter simulations \citep{V14a,V12}. The reason for the conflicting results between the flux-ratio anomaly and gravitational imaging techniques is currently not clear.  While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than substructure \citep[see][for a discussion]{Xu15}.

@@

Here we focus on CLASS B1555+375 \citep{Marlow99}, which was discovered as part of the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2}. B1555+375 has four lensed images with a maximum separation of 426~mas in a fold-configuration, where the two merging lensed images show a strong and persistent flux-ratio anomaly at radio wavelengths; previous radio monitoring observations ruled out microlensing effects as the cause of the anomaly \citep{K03}. As B1555+375 was included in the observational and theoretical analyses of both \citet{Dalal2002} and \citet{Xu15}, understanding its mass distribution is of key importance to assess any systematics with the inferred level of substructure in the lensing halo with the flux-ratio anomaly method. The SHARP imaging data are introduced in Section 2 and we present a revised lens model using these data in Section 3. The results of this analysis and their implications are discussed in Section 4. Note that the redshifts of both the lens galaxy and the lensed source are unknown for B1555+375, so we assume redshifts of $z_l = 1$ and $z_s = 1.5$, respectively, due to their red colours \citep{Marlow99}. This assumption has no effect on the derived magnifications or flux-ratios of our analysis.

@@

Our dataset consists of optical and infrared imaging taken with the W. M. Keck-II Telescope and the Hubble Space Telescope ({\it HST}), and high-resolution radio imaging taken with the Very Long Baseline Array (VLBA), which are discussed below and are summarized in Table~\ref{tab:obs}.

@@

There are several notable features in the high-resolution AO and {\it HST} data. These include the nearly complete lack of emission associated with lensed images B and D (see Fig.~\ref{fig:merlin} ), as can be seen by comparing the radio contours to the $K^\prime$-band emission, and the faint, but clearly visible emission from what appears to be an edge-on lensing galaxy, with a position angle of $\sim 10$~deg and an ellipticity ($e$, define as the axis ratio $q=1-e$) of $\sim 0.8$. We note that this position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D. Therefore, the lack of emission that is seen from these images is likely due to dust extinction and additional demagnification due to lensing.

@@

The flux-ratio anomaly and relative sizes of the images at radio-wavelengths implies that there must be some form of perturbation to the gravitational lens mass model, which has thus far been attributed to dark matter substructure within the lensing galaxy or along the line-of-sight to the lensed images \citep{Dalal2002,Xu12,Xu15}. However, our high-resolution near infrared imaging suggests the intriguing possibility that the mass perturbation could be due to an edge-on disc component within the lens. To test this possibility, we model the system with a disc component in order to see if a plausible mass model can explain the flux-ratio anomaly, without the need for additional substructure.

We use the lens modelling code {\sc gravlens} \citep{Kee01} to model the compact radio components. The inputs to the model are the observed image positions measured from the MERLIN radio observations of \citet{Marlow99} as all of the images are significantly detected in these data. The flux-ratio measurements are taken from \citet{K03}, who used half a year of MERLIN monitoring to obtain flux-ratio curves. In total, there are 11 constraints to the mass model provided by the observational data. As a first trial of modelling, we re-create the singular isothermal ellipsoid without external shear (SIE; 7 free parameters) model of \citet{Marlow99} to check the performance of a simple lensing potential. Consistent with previous studies \citep{Marlow99,Xu15}, a single elliptical potential model cannot reproduce the observed flux-ratios in B1555+375 (see Table~\ref{tab:results}; reduced $\chi^2 =97.3$).

The next step is to examine if an edge-on disc can cause a physically plausible perturbation in the strong lensing mass model that results in the observed flux ratio anomaly of  merging images A and B. An exponential disc profile best describes the disc component in spiral galaxies because it matches the light distribution \citep{Kee98}. We thus choose a SIE plus an exponential disc model (SIE+ExpDisc) in our study of B1555+375. The free parameters of the model are the SIE Einstien radius ($b$), centroid position, ellipticity ($e$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$), and scale length ($R_s$). A Detailed definition of these mass profiles is described by \citet{Kee01}. The source position adds two additional model parameters. We have not included a third component such as an external shear or an NFW halo because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model. Significantly deeper observations at a higher bandwidth with current very long baseline interferometric arrays can test more complex models in the future by imaging the extended gravitational arc and more significantly detecting image D.

@@

The best-fit model parameters and 68\% CL errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:model}. Table \ref{tab:results} also shows the comparison between the observed radio data and the model predicted image positions and flux ratios. We find that by adding an elongated exponential disc to a smooth potential model there is significant improvement in the predicted flux-ratios when compared to the results for the SIE-only model, with a reduced $\chi^2 = 2.7$. The positions are all in agreement, and the flux-ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B. The differences in fluxes may due to the source could be slightly extended sphere while our model uses point-source. The mass model requires that the exponential disc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable. We note that there is a significant 0.036~arcsec offset between the SIE and exponential disc components, which is likely due to there being an additional ellipticity in the model (e.g. from an external shear) that is being partly compensated for by the disc component. Again, more complex mass models that use the full extent of the gravitational arc and the compact lensed images from future high resolution radio imaging will be able to confirm this.

@@

Although flux-ratio anomalies provide a powerful tool to investigate low-mass substructure in lensing haloes out to cosmological redshifts, it is clear that some care is needed in interpreting the results. It is now well established that observations of radio-loud gravitational lenses provide the most robust observational constraints because they are less affected by dust extinction and microlensing, and monitoring can determine the best estimate of the intrinsic flux ratios. This has led to an often studied sample of eight radio-loud gravitational lenses with well-defined flux-ratio measurements that are most likely due to perturbations in forms of clumpiness from a smooth mass distribution \citep{Dalal2002,KD04,Xu15}. In general, lens models that are based only on the locations of lensed radio-loud images have large degeneracies due to the limited number of constraints that are provided by 50 to 200~mas imaging of the unresolved sources \citep[e.g.][]{Ka91}. Furthermore, the nature of the perturbation may not be due exclusively to a population of low-mass "dark" substructures as has been already shown to be the case for MG J0414+0534 and MG J2016+112, where there is evidence for luminous companion dwarf galaxies that can account for the observed flux ratios, and even observed astrometric anomalies (\citealt{ros00,chen07,more09}; see also \citealt{mckean07,jackson10}).

Here, we find evidence for an edge-on disc in the flux-ratio anomalous gravitational lens B1555+375 that can also account for the required perturbation in the mass model. Such high-order deviations from a smooth mass distribution have already been suggested \citep{evans03,congdon05}, but this is the first time that a disc has been observed and modelled to account for a flux-ratio anomaly. However, it is important to realise that by including observationally motivated perturbations like luminous dwarf companions or edge-on discs in the mass models, we are still limited in our interpretation since we must assume that the anomalies are due exclusively to these additional components. For B1555+375, it may be possible to independently constrain the mass of the disc through kinematic measurements (most likely from mm-wavelength resolved emission line observations), which would test whether the disc makes a sufficient contribution to the mass model (e.g. as in the case of B1933+503; \citealt{suyu12}). Also, as we have shown here, B1555+375 shows evidence for an extended $\sim100$~mas gravitational arc at radio-wavelengths that crosses the edge-on disc. Further high resolution imaging with very long baseline interferometry will provide the observational constraints required to fully test whether the extended disc is sufficient to cause the anomaly. Nevertheless, before concluding that the flux-ratios in any given lens system are a result of substructure, it is critical to explore a range of smooth models that are informed by additional observations or to do a comprehensive analysis such as that conducted by \citet{Xu15}. Otherwise, the derived substructure fractions should be considered as upper limits.

@@

%In this letter, we instead focus on the effect that more complicated lens galaxy mass distributions \textbf{have} on flux-ratio anomalies. Traditionally, flux-anomalous lensed quasars have been radio-loud, initially discovered in radio observations. While radio data provide reliable information on the positions and the fluxes of the lensed images, they are often unable to detect the lens galaxies. Moreover, lens modelling based only on the positions of the four images can be highly degenerate and prior assumptions play a key role in the interpretation of the observed flux-ratio anomaly.  Since lens galaxies are typically at redshifts of $z \leq 1$, optical and near-infrared observations are ideal for measuring the light distribution of lens galaxies and obtaining useful prior information on the underlying mass distributions. Indeed \citet{SHARP12} showed that high resolution IR imaging can help to significantly improve the precision of the lens modelling. This improvement is even more dramatic in the case of B1555+375, where HST and SHARP AO high resolution imaging has allowed us to detect, for the fist time, the presence of an edge-on disk. This newly discovered edge-on disk provides a strong prior for our lens modelling.  With an additional disk component, our model matches to both the radio image positions and their flux-ratio, wheras models with only one SIE component \citep{Marlow99,Xu15} fail to reproduce the fluxes correctly. Our successful modelling indicates that the kpc-scale structure of the lens galaxy itself is sufficient to explain the flux-ratio anomalies in B1555+375, without any need to invoke the presence of substructure.

%From a theoretical perspective, \citet{Xu15} also find that substructures cannot explain the observed radio flux anomalies in all the gravitational lenses that were considered. After adding sub-haloes from numerical simulations to these systems, only one out of the eight radio-loud gravitational lenses achieves the level of the flux-ratio anomalies seen in the observations.  The rest are unlikely (only $1 - 4$ per cent probability) to have an observed distribution of flux-ratio anomalies produced only by substructure, including our target B1555+375. In fact, among those eight radio lenses, B1555+375 is one of the most anomalous gravitational lenses, but it is also one of the most challenging systems to explain by substructures. \citet{Xu15} have concluded that the failure in predicting flux-ratios is most likely due to an oversimplified/improper lens modelling, which is consistent with the results of this letter. They also point out that the SIE component and the external shear in their model are orthogonal, indicating a possible missing ingredient in the lens model. Indeed, it's hard to find physical interpretation for an large and orthogonal external shear, without the inclusions of an observationally motivated edge-on disc component.

Our results for B1555+375 clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies. While upcoming large-scale surveys with the Dark Energy Survey, Kilo-Degree Sky-VIKING, Square Kilometre Array, {\it Euclid}, and Large Synoptic Survey Telescope, are expected to deliver new large samples of gravitationally lensed quasars, in the near future the discovery of new systems using narrow-line quasar emission \citep{N14} will provide a new and invaluable statistical perspective on the current constraints based on flux-ratio anomalies. We stress, therefore, that one should be very careful when interpreting the nature of flux-ratio anomalies, as prior simple assumptions on the lens mass distribution are a significant source of bias.

Our analysis shows that in order to derive a precise quantification of the substructure population and any derived properties from strongly lensed flux-ratio anomalies, it is crucial to have a careful estimation of non-substructure effects, such as galaxy discs and nearby massive satellites. In fact, even in the presence of mass substructures, the observed flux-ratio anomalies could be still affected by the complex structure of the lens galaxy. Finally, additional near-infrared AO imaging from SHARP shows that B1555+375 is not the only gravitational lens having a significant disc component detection in the lensing galaxy.  These gravitational lenses will be investigated in a future work, but the images alone strongly suggest that other systems may have similar links between flux-ratio anomalies and disc components.
